Fusing Filters with Integer Linear Programming

### 2014-05-16 2014betterfusionforfilters/section/03-SizeInference.tex
mention size inf failure
size inf fail
spacing and typo

%!TEX root = ../Main.tex
\section{Size Inference}
Before performing fusion proper, we must infer the relative sizes of each array in the program. We achieve this with a simple constraint based inference algorithm, which we discuss in this section. Size inference has been previously described in the context of array fusion by Chatterjee~\cite{chatterjee1991size}. In constrast to our algorithm, \cite{chatterjee1991size} does not support size changing functions such as filter.

@@

For example, the final environment and constraints generated for the @normalize2@ example from Section~\ref{s:Introduction} are as follows:
$$
\begin{array}{ll}
       & x : k_{xs},~ gts : k_{gts},~ \exists k_1,~ k_2,~ k_3 
\\
\vdash & \true 
        ~\wedge~  k_{gts} = k_1
        ~\wedge~  \true
\\     &~~~~~~~~ 
          \wedge~  k_{xs}  ~= k_2
        ~ \wedge~  k_{ys1}  = k_2 
        ~ \wedge~  k_{xs}   = k_3
        ~ \wedge~  k_{ys2}  = k_3
\end{array}
$$
Rule~(SFun) also characterises the functions we accept: A function is \emph{valid} if and only if $\exists \sigma. \SizeF{\function}{\sigma}$.

@@

To produce the final size scheme, we lookup the sizes of the input and output variables of the original function from the solved constraints and generalize appropriately. This process is determined by the top-level rule in Figure~\ref{f:ConstraintGeneration}. In this case, no rigid size variables appear in the result, so we can universally quantify all size variables.
$$@normalize2@ ~:_s \forall k. (xs : k) \to (ys_1 : k,~ ys_2 : k)
$$

>>>>

%!TEX root = ../Main.tex
\section{Size Inference}
Before performing fusion proper, we must infer the relative sizes of each array in the program. We achieve this with a simple constraint based inference algorithm, which we discuss in this section. Size inference has been previously described in the context of array fusion by Chatterjee~\cite{chatterjee1991size}. In constrast to our algorithm, \cite{chatterjee1991size} does not support size changing functions such as filter.
If size inference fails, the programs may still be compiled, but fusion is not performed.

@@

For example, the final environment and constraints generated for the @normalize2@ example from Section~\ref{s:Introduction} are as follows:
$$
\begin{array}{ll}
       & x : k_{xs},~ gts : k_{gts},~ \exists k_1,~ k_2,~ k_3 
\\
\vdash & \true 
        ~\wedge~  k_{gts} = k_1
        ~\wedge~  \true
\\     &~~~~~~~~ 
          \wedge~  k_{xs}  ~= k_2
        ~ \wedge~  k_{ys1}  = k_2 
        ~ \wedge~  k_{xs}   = k_3
        ~ \wedge~  k_{ys2}  = k_3
\end{array}
$$
Rule~(SFun) also characterises the functions we accept: A function is \emph{valid} if and only if $\exists \sigma.\ \SizeF{\function}{\sigma}$.

@@

To produce the final size scheme, we look up the sizes of the input and output variables of the original function from the solved constraints and generalize appropriately. This process is determined by the top-level rule in Figure~\ref{f:ConstraintGeneration}. In this case, no rigid size variables appear in the result, so we can universally quantify all size variables.
$$@normalize2@ ~:_s \forall k. (xs : k) \to (ys_1 : k,~ ys_2 : k)
$$
